Characterizing dynamical transitions by statistical complexity measures based on ordinal pattern transition networks

### 2020-10-30 manuscript_Huang.tex
further changes made on Friday.

\section{Transitions in continuous system}
The previous results have been further verified in the chaotic R\"ossler system \cite{Roessler1976}, namely, $(\dot{x}, \dot{y}, \dot{z}) = (-y-z, x+0.2y, b+z(x-5.7))$, where $b$ is the control parameter. There are some challenging problems for constructing OPTNs for time series from continuous systems.

>>>>

\section{Transitions in continuous system}
The previous results have been further verified in the chaotic R\"ossler system \cite{Roessler1976}, namely, $(\dot{x}, \dot{y}, \dot{z}) = (-y-z, x+0.2y, b+z(x-5.7))$, where $b$ is the control parameter. There are some challenging problems for constructing OPTNs for time series from continuous systems, for instance, proper choice of sampling frequency and embedding parameters, which must depend on the particular time scales of the system. {\color{red} numerical details will be provided soon. }
